Manuscript Figures for Genome Biology

### 2018-10-12 manuscript_figures/manuscript_figures.Rmd
Fix axis label in Fig1

# Figure 2C: ROC curve
p3 <- plotsim_average(res5d, met=c("FPR", "TPR"),filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      #ylab("Number of Rejections") +
      ggtitle("ROC (FPR vs TPR)") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

>>>>

# Figure 2C: ROC curve
p3 <- plotsim_average(res5d, met=c("FPR", "TPR"),filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ggtitle("ROC (FPR vs TPR)") +
      scale_x_continuous("FPR", breaks=seq(0, 1, by=0.01))
